\section{\ml{Skills}{Conocimientos}}

\cvitem{}{\ml
    % EN
    {My main areas of knowledge are the following:}
    % ES
    {Mis areas de conocimiento son principalmente las siguientes:}}

\cvcomputer
    {\ml{Programming Languages}{Lenguajes de programación}}
        {\textbf{Python (last $\sim$8 years)}
        \\ Java and C\# (5 years before that)
        \\ C/C++ (~6 years mostly in college; barely any professional experience).
        \\ Currently \textbf{learning Go and Rust} with no professional experience.
        \\ Touched many others: JS/TS for React, asm, Objective-C, PHP...}
    {\ml{Infrastructure}{Infraestructura}}
        {\textbf{AWS}: ECS, EC2, Lambda, API Gateway, Athena, Kinesis, SQS, DynamoDB, etc. \\
        Proficiency at Docker and docker-compose. Knowledge of CDK}

%--

\cvcomputer
    {Web servers and frameworks}
        {Fast API, flask, AWS powertools. Mostly forgotten: Ext.Net, Django, nextjs...}
    {\ml{CI/CD}{CI/CD}}
        {Gitlab-CI, Github actions. Proficiency at Git.}

%--

\cvcomputer
    {\ml{Software Design}{Diseño de Software}}
        {\ml
            % EN
            {Good practices on (real world) object oriented design, SOLID
            principles and design patterns. \\ \textbf{Big Advocate for TDD},
            which I practice every day for almost a decade.}
            % ES
            {Buenas prácticas de diseño orientado a objetos, principios SOLID y
            patrones de diseño. \\ \textbf{Gran defensor de TDD/BDD}, el cual
            practico a diario desde hace casi una década.}
        }
    {\ml{Testing Libraries}{Bibliotecas de testeo}}
        {\ml
            {\textbf{mostly Pytest}, python's unittests, Behave, Xunit, JUnit, Mocha, etc}
            {\textbf{principalmente Pytest}, unittests, Behave, Xunit, JUnit, Mocha, etc}
        }


%--

\cvcomputer
    {OS}
        {\ml
            % EN
            {Advanced knowledge of GNU/Linux, as a daily user (for about 20
            years), and some knowledge as administrator (proficient at bash
            scripting, CLI, services, cronjobs, etc). Also worked with Windows
            Server, IIS etc in the past, must most comfortable on Linux.}
            % ES
            {Conocimientos avanzados a nivel de usuario de GNU/Linux (19 años
            de uso diario) y conocimientod nivel medio como administrador (bash
            scripting, servicios, cronjobs, etc). También he trabajado con
            Windows Server, IIS etc, aunque no es mi punto fuerte.}
        }
    {DB}
        {SQL/T-SQL: Oracle, Postgress, MicroSoft SQL Server, MySQL. \\ NoSQL:
        DynamoDB and ElasticSearch maily, a little of MongoDB.}
