%% Inicio del archivo `template-es.tex'.
%% Copyright 2006-2012 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.

% opciones posibles incluyen tamaño de fuente ('10pt', '11pt' and '12pt'),
% tamaño de papel ('a4paper', 'letterpaper', 'a5paper', 'legalpaper',
% 'executivepaper' y 'landscape') y familia de fuentes ('sans' y 'roman')
\documentclass[11pt,a4paper,sans]{moderncv}   

% Temas de moderncv

% Las opciones de estilo son 'casual' (por omision) y 'classic' 
\moderncvstyle{casual}                        
% Opciones de color 'blue' (por omision), 'orange', 'green', 'red', 'purple', 'grey' y 'black'
\moderncvcolor{blue}                          

% Para seleccionar la fuente por omision, use '\sfdefault' para la fuente sans
% serif, '\rmdefault' para la
%\renewcommand{\familydefault}{\sfdefault}

%fuente roman, o cualquier nombre de fuente
% Elimine el comentario para suprimir la numeracion automatica de las paginas
% para CVs mayores a una pagina
%\nopagenumbers{}

% codificacion de caracteres
% Reemplace con su codificacion
\usepackage[utf8]{inputenc}                   
\usepackage[english]{}
% Si necesita usa CJK para redactar su CV en chino, japones o coreano
%\usepackage{CJKutf8}                         

% Ajustes para los margenes de pagina
\usepackage[scale=0.75]{geometry}

\hyphenation{assem-bler}

% To change the column width for dates
%\setlength{\hintscolumnwidth}{3cm}           

%----------------------
% PERSONAL INFORMATION
%----------------------
\firstname{José Ramón}
\familyname{Cano Yribarren}
\title{Software Engineer}                                % optional
\address{Noordwal 68}{Den Haag, 2513EC (The Nederlands)} % optional
\mobile{+31~(0)6~51~03~04~66}                            % optional
% \phone{+34~958~508~130}                                % optional
% \fax{+3~(456)~789~012}                                 % optional
\email{joserc87@gmail.com}                               % optional
% \homepage{http://joseramoncano.com}                    % optional
% \extrainfo{informacion adicional}                      % optional

% PICTURE (optional):
% '64pt' is the height to which the image will be adjusted, and 0.4pt is the
% frame width containing it (set it to 0pt to remove the frame). 'picture' is
% the name of the fileis the height to which the image will be adjusted, and
% 0.4pt is the frame width containing it (set it to 0pt to remove the frame).
% 'picture' is the name of the file
% \photo[64pt][0.4pt]{picture}
% \quote{some optional quote}                            % optional

% To show numeric labels in the bibliography (by default they are not shown).
% Only useful when you add quotes in your CV
%\makeatletter
%\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
%\makeatother

% Bibliography with multiple sources
%\usepackage{multibib}
%\newcites{book,misc}{{Libros},{Otros}}

%---------
% CONTENT
%---------
\begin{document}
%\begin{CJK*}{UTF8}{gbsn}                     % para redactar el CV en chino usando CJK
\maketitle

\section{Personal information}
\cvitem{First Name}{José Ramón}
\cvitem{Last Name}{Cano Yribarren}
\cvitem{Gender}{Male}
\cvitem{Nationality}{Spanish}
\cvitem{Marital status}{Single}
\cvitem{Age}{28}
\cvitem{E-mail}{joserc87@gmail.com}

\section{Languages}
\cvitemwithcomment{Spanish}{Native}{}
\cvitemwithcomment{English}{Second language}{}
\cvitemwithcomment{Dutch}{Very basic}{}

\section{Experience}
\cventry{2012--Present}{Software engineer/developer at R\&D}{The Consultancy Firm}{The Netherlands}{}{}

\section{Education}
\cventry{2005--2011}{Engineering in software and computer science}{University of Granada}{Spain}{}{}
\cventry{2003--2005}{Science high school diploma}{Instituto Padre Manjón}{Granada}{Spain}{}
%\cventry{a\~no--a\~no}{Grado}{Instituci\'on}{Ciudad}{\textit{Grade}}{Descripci\'on}

%\section{Tesis de maestr\'ia}
%\cvitem{t\'itulo}{\emph{T\'itulo}}
%\cvitem{sinodares}{Sinodales}
%\cvitem{descripci\'on}{Una breve descripci\'on de la tesis}

% \section{Experiencia}
% \subsection{Vocacional}
% \cventry{a\~no--a\~no}{t\'itulo del puesto}{Empleador}{Ciudad}{}{Descripci\'on general, no m\'as de 1 \'o 2 l\'ineas.\newline{}%
% Detalle de logros:%
% \begin{itemize}%
% \item Logro 1;
% \item Logro 2, con sub-logros:
%   \begin{itemize}%
%   \item Sub-logro (a);
%   \item Sub-logro (b), con sub-sub-logros (¡evite hacer esto!);
%     \begin{itemize}
%     \item Sub-sub-logro i;
%     \item Sub-sub-logro ii;
%     \item Sub-sub-logro iii;
%     \end{itemize}
%   \item Sub-logro (c);
%   \end{itemize}
% \item Logro 3.
% \end{itemize}}
% \cventry{a\~no--a\~no}{t\'itulo del puesto}{Empleador}{Ciudad}{}{Descripci\'on l\'inea 1\newline{}Descripci\'on l\'inea 2}
% \subsection{Miscel\'aneo}
% \cventry{a\~no--a\~no}{t\'itulo del puesto}{Empleador}{Ciudad}{}{Descripci\'on}


\section{Scholarships and awards}
\cventry{2011}{Final year project}{VOLUME RAY-CASTING}
	{Engineering in software and computer science, University of Granada}{Grade: 10}
	{Implementation of a real time volumetric Ray-Casting renderer in GPU.} %\hfill{\itshape\color{see}\footnotesize{}Visite www.maquinafalsa.es/portalfisica}.
\newpage

\section{Knowledge}
\cvitem{}{My main areas of knowledge are the following (items are listed in descending order of experience):}

\cvcomputer
	{Programming Languages}{C/C++, Java, C\#, Objetive-C, Asm, Python, PHP, JS,
VB.Net, Ruby, Haskell.}
	{Technologies}{XML (DOM, SAX, XPath, Serialization/Marshalling), WebServices (SOAP/REST), LDAP.}
\cvcomputer
	{Web Frameworks}{Ext.Net. Others: Laravel, Django}
	{GUIs}{Swing, Cocoa Touch, Qt, SDL.}
\cvcomputer
	{Software Design}{UML, Object Orientation, Design Patterns, TDD/BDD, data
structures and algorithms, CVS (git/svn).}
	{Libraries}{Xunit, JUnit}
\cvcomputer
	{Artificial Intelligence and Soft Computing}{Bio-inspired and evolutionary
algorithms, Artificial Neural Networks (Matlab), Computer Vision (OpenCV),
Pattern Recognition, System Simulation.}
	{Parallel Programming}{MPI, OpenMP, OpenCL, Threads.}
\cvcomputer
	{OS}{Advanced use of GNU/Linux, *nix CLI and kernel compiation. Windows at
user level and MS-DOS scripting.}
	{DB}{SQL/T-SQL, MicroSoft SQL Server, MySQL, Oracle.}
\cvcomputer
	{Electronics}{Pic/AVR microcontrolers programming, just as a hobby. PLCs
programming. Base knowledge of electronics.}
	{Computer Graphics}{OpenGL (VBO, DL, FBO, GLSL), raytracing,
volumetric-raycasting.}
\cvcomputer
	{IDEs}{VisualStudio, Vim, Eclipse, IntelliJ IDEA, Netbeans, QtCreator,
Code::Blocks}
	{Other Software}{Vim, Emacs, Git, Svn, Tmux, Makefile, GNU AutoTools, Doxygen,
Lex, Yacc, Doxygen, GNU-plot}
\cvcomputer
	{Office}{\LaTeX, LyX, OpenOffice, Microsoft Office.}
	{Other Skills}{Problem Solving. Mathematical thinking and notation.
Abstract thinking. Team work. Ease of learning \& curiosity.}

%\section{Conocimientos de computaci\'on}
%\cvdoubleitem{categor\'ia 1}{XXX, YYY, ZZZ}{categor\'ia 4}{XXX, YYY, ZZZ}

\section{Projects @ The Consultancy Firm}
\cvitem{The Document Wizard}{A web application written in C\# using ASP,
Ext.Net, MicroSoft SQL Server, ActiveDirectory, WCF, etc. This application
connects to \textit{OpenText}'s \textit{Stream Server} via it's SOAP API to
generate documents based on answers to dynamic questions.}
\cvitem{DocWiz}{An iOS app written in Objective-C that works as an online or
offline client for The Document Wizard.}
\cvitem{Augmented Documents}{An augmented reality app for iOS using OpenGL, and
MetaIO SDK.}
\cvitem{The Apprentice}{An intuitive WYSIWYG editor written in Java, with Swing
for the GUI, to generate "Question" configurations for The Document Wizard.
Those configurations are marshalled to a file or directly uploaded with SOAP.}
\cvitem{Sandd Connector}{A \textit{StreamServe} connector written in Java that reads the
network of physical addresses (houses) provided by Sandd and executes a
sorting/classification algorithm on the printing queue so the letters are printed
in the order in which Sandd will deliver them, to minimize the costs.}
\cvitem{PDF connector}{A \textit{StreamServe connector} written in Java and
using PDFBox to fix `faulty' PDF output that \textit{StreamServe} generates.}
\cvitem{PS connector}{A \textit{StreamServe connector} written in Java that
parses PostScript output to fix problems in its fonts.}
\cvitem{ASure}{A notification connector in Java for error reporting to a
MicroSoft SQL Server database using JDBC}

\section{Areas of interest}
\cvlistdoubleitem{Software development}{Graphics programming}
\cvlistdoubleitem{Intelligent systems and robotics}{Embedded systems programming}
\cvlistdoubleitem{Mobile devices programming}{}

\section{Other interests}
\cvlistdoubleitem{Music}{Aeronautics}
\cvlistdoubleitem{Sports(tennis, basketball)}{Pinballs}

% \section{Extra 1}
% \cvlistitem{Tema 1}{Tema2.1}
% \cvlistitem{Tema 2}
% \cvlistitem{Tema 3}

\renewcommand{\listitemsymbol}{-~}            % To change the simbol for lists

% Las publicaciones tomadas de un archivo de BibTeX sin usar multibib\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}

%\nocite{*}
%\bibliographystyle{plain}
%\bibliography{publications}                   % 'publications' es el nombre del archivo BibTeX

% Las publicaciones tomadas de un archivo BibTeX usando el paquete multibib
%\section{Publicaciones}
%\nocitebook{book1,book2}
%\bibliographystylebook{plain}
%\bibliographybook{publications}              % 'publications' es el nombre del archivo BibTeX
%\nocitemisc{misc1,misc2,misc3}
%\bibliographystylemisc{plain}
%\bibliographymisc{publications}              % 'publications' es el nombre del archivo BibTeX

%\clearpage\end{CJK*}                          % si esta redactando su CV en chino usando CJK, \clearpage es requerido por fancyhdr para que funcione correctamente con CJK, aunque esto eliminara la numeracion de pagina al dejar \lastpage como no definido
\end{document}


%% fin del archivo `template-es.tex'.
